---
title: "PTGER2 & PTGER4 Grouping and analysis"
author: "Siwakorn P"
date: "2024-04-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Library
```{r}
library(Seurat)
library(tidyverse)
library(harmony)
library(scales)
library(fgsea)
library(msigdbr)
library(biomaRt)
library("org.Mm.eg.db")
library(extrafont)
```

#Load Dataset
Integrated data was derived from: 1_Data_Integration_and_Annotation.Rmd
```{r}
Integrated = readRDS("YourWorkingDirectory/Demo.Integrated.rds")
```
#------------------

#Instant command
##PTGER4 Grouping
```{r}
PTGER4.Group = function(Obj1, Identity = "Identity.Celltype", Batch = "Batch.scRNA"){
      df = data.frame()
      Cluster = unique(Obj1[[]][,Identity]) %>% as.character()
      Idents(Obj1) = Identity
      for(i in Cluster){
            Obj2 = subset(Obj1, idents = i)
            AllBatch = unique(as.character(Obj2[[]][,Batch] ))
            for(j in AllBatch ){
                  Idents(Obj2) = Batch
                  Obj3 = subset(Obj2, idents = j)
                  tmp = FetchData(Obj3, vars = "PTGER4",slot="data") %>% arrange(desc(PTGER4))
                  tmpA = filter(tmp,PTGER4 == 0)
                  tmp = filter(tmp,PTGER4 != 0)
                  if(nrow(tmpA) > 0 ) {
                        tmpA$PTGER4.Group = "Undetected"
                        } 
                  if(nrow(tmp) > 0 ) {
                        tmp$PTGER4.Group = "Low"
                        tmp$PTGER4.Group[1:round(nrow(tmp)/3)] = "High" 
                        tmp$PTGER4.Group[(round(nrow(tmp)/3)+1):(round(nrow(tmp)/3*2))] = "Intermediate"
                        }
                  tmp = rbind(tmp,tmpA)
                  if(nrow(tmp) > 0 ) {
                        tmp$Cluster = i
                        tmp$Batch = j
                        }
                  print(paste0(i," ",j, " ... ", (nrow(tmp) == ncol(Obj3)  ) ) )
                  df = rbind(df,as_tibble(tmp,rownames="CB"))
            }
      }
      print(paste0("Validation : ", nrow(df) == nrow(Obj1[[]]) ) )
      tmp2 = df$PTGER4.Group
      names(tmp2) = df$CB
      return(tmp2)
}
```

##PTGER2 Grouping
```{r}
PTGER2.Group = function(Obj1, Identity = "Identity.Celltype", Batch = "ID"){
      df = data.frame()
      Cluster = unique(Obj1[[]][,Identity]) %>% as.character()
      Idents(Obj1) = Identity
      for(i in Cluster){
            Obj2 = subset(Obj1, idents = i)
            AllBatch = unique(as.character(Obj2[[]][,Batch] ))
            for(j in AllBatch ){
                  Idents(Obj2) = Batch
                  Obj3 = subset(Obj2, idents = j)
                  tmp = FetchData(Obj3, vars = "PTGER2",slot="data") %>% arrange(desc(PTGER2))
                  tmpA = filter(tmp,PTGER2 == 0)
                  tmp = filter(tmp,PTGER2 != 0)
                  if(nrow(tmpA) > 0 ) {
                        tmpA$PTGER2.Group = "Undetected"
                        } 
                  if(nrow(tmp) > 0 ) {
                        tmp$PTGER2.Group = "Low"
                        tmp$PTGER2.Group[1:round(nrow(tmp)/2)] = "High" 
                        }
                  tmp = rbind(tmp,tmpA)
                  if(nrow(tmp) > 0 ) {
                        tmp$Cluster = i
                        tmp$Batch = j
                        }
                  print(paste0(i," ",j, " ... ", (nrow(tmp) == ncol(Obj3)  ) ) )
                  df = rbind(df,as_tibble(tmp,rownames="CB"))
            }
      }
      print(paste0("Validation : ", nrow(df) == nrow(Obj1[[]]) ) )
      tmp2 = df$PTGER2.Group
      names(tmp2) = df$CB
      return(tmp2)
}
```

##DE analysis 
```{r}
FullDE <- function(Obj,Group = "PTGER4.Group", Batch = "ID",A = "High", B = "Low"){
      DE = list()
      Idents(Obj) = Batch
      for(i in unique(Obj[[]][,Batch]) ){
            tmp = subset(Obj, idents = i)
            print(paste0(i," : ", ncol(tmp), " Cells"))
            tryCatch({
                  Idents(tmp) = Group
                  print(summary(Idents(tmp)))
                  DE[[i]] = FindMarkers(tmp,ident.1 = A, ident.2 = B, logfc.threshold = 0,min.pct =0.01 )
            }, error = function(e){print(e)})
      }
      #Sum table
      df = data.frame()
      for(i in names(DE) ){
            tmp = DE[[i]] %>% as_tibble(rownames = "Genes") %>% dplyr::select(Genes, avg_log2FC)
            tmp$Datasets = i
            df = rbind(df,tmp)
      }
      df = spread(df, Genes, avg_log2FC) %>% as.data.frame()
      rownames(df) = df$Datasets
      df = dplyr::select(df,-Datasets)
      df2 = matrix(nrow = ncol(df),ncol=0) %>% data.frame()
      rownames(df2) = colnames(df)
      df2$Upregulation = "NA"
      df2$Downregulation = "NA"
      for(i in colnames(df)){
            tmp = df[,i] > 0 
            df2[i,"Upregulation"] = sum(tmp)
            tmp = df[,i] < 0 
            df2[i,"Downregulation"] = sum(tmp)
      }
      df2$Upregulation = as.numeric(df2$Upregulation)
      df2$Downregulation = as.numeric(df2$Downregulation)
      DE[["FoldChange.Table"]] = df
      DE[["FoldChange.Sum"]] = df2
      return(DE)
}
```

#PTGER2/4 Grouping
Running time: 18 seconds (on Apple MacBook Air M2 16GB RAM, macOS 14.4.1)

Funtion PTGER4.Group() divides cells in each cell type in each specimen/batch (ID) into PTGER4 high, PTGER4 intermediate, and PTGER4 low equally
Output: A vector contains PTGER4 group and cell barcode index

Funtion PTGER2.Group() divides cells in each cell type in each specimen/batch (ID) into PTGER2 high and PTGER2 low equally
Output: A vector contains PTGER2 group and cell barcode index
```{r}
tmp = PTGER4.Group(Integrated,Identity = "Identity.Celltype",Batch = "ID")
Integrated = AddMetaData(Integrated,metadata = tmp, col.name = "PTGER4.Group")
Integrated$PTGER4.Group = factor(Integrated$PTGER4.Group, levels = c("Undetected", "Low","Intermediate","High"))

tmp = PTGER2.Group(Integrated,Identity = "Identity.Celltype",Batch = "ID")
Integrated = AddMetaData(Integrated,metadata = tmp, col.name = "PTGER2.Group")
Integrated$PTGER2.Group = factor(Integrated$PTGER2.Group, levels = c("Undetected", "Low","High"))
```

##DE analysis (PTGER4Hi - PTGER4Lo)
Running time: 3 minutes (on Apple MacBook Air M2 16GB RAM, macOS 14.4.1)
Function FullDE() computes DE Genes between population A (PTGER4 Hi) and population B (PTGER4 Lo)
- Group: PTGER4 group name
- Batch: specimen ID
Expected output: a list with DE genes in each cell type

```{r}
DE = list()
Idents(Integrated) = Integrated$Identity.Celltype
selected.clusters = c("NK cell","CD8 T cell","CD4 T cell", "Regulatory T cell","Neutrophil","Monocyte")
for(i in selected.clusters ){
      print(i)
      tmp = subset(Integrated, idents = i)
      DE[[i]] = FullDE(tmp, Group = "PTGER4.Group", Batch = "ID" , A = "High", B = "Low" )
}
```

###Create a single table of DE genes 
```{r}
df = data.frame()
for(i in names(DE)){
  tmp = names(DE[[i]]) %>% setdiff(c("FoldChange.Table","FoldChange.Sum"))
  for(j in tmp ){
      df1 = DE[[i]][[j]] %>% as_tibble(rownames = "Genes")
      df1$Cluster = i
      df1$Dataset = j
      df = rbind(df,df1)
      }
}
df$Cluster = factor(df$Cluster, levels= names(DE) )
DE$df = df
```

###Plot Heatmap
```{r}
selected.cluster = c("CD8 T cell")
for(i in c("CD8.Overview3") ){
  selected.genes = unlist( GeneSet$DE[[i]] ) %>% unique()
  df1 = filter(df, Genes %in% selected.genes )  %>% filter(Cluster %in% selected.cluster)
  df1 = GeneGroup(df1, GeneSet$DE[[i]] )
  Fsize = 6
  a = max(abs(df1$avg_log2FC))+0.2 
  plot = ggplot(df1, aes(y = Dataset , x = Genes  ) ) + 
    facet_grid(Cluster ~ Set, scales = "free", space="free", switch = "y") + 
    theme_classic() + 
    Dot_axis90A + 
    ggtitle(i)+
    geom_tile(color = "white",aes(fill =avg_log2FC)) +  
    scale_fill_gradientn(colours = Col.HiLow.9Shades,
                         values =  c( 0,0.43,0.5,0.57,  1 ),                                 
                         limits = c(-a,a) ) +
    theme(plot.title = element_blank(),
          axis.text.x = element_text(size =Fsize, family = "Arial", color = "black", face = "italic",angle = 90, hjust =1, vjust =0.3),
          axis.text.y = element_text(size =Fsize, family = "Arial", color = "black"),
          axis.line = element_line(colour = 'black', size = 0.25),
          axis.ticks = element_line(colour = 'black', size = 0.15),
          axis.ticks.length = unit(0.05,"cm"),
          axis.title = element_blank(), 
          strip.text.y = element_blank(),
          strip.text.x.top = element_text(size =Fsize, family = "Arial",colour = "black",
                                          margin = margin(t = 0.1, r = 0, b = 0.1, l = 0, unit = "cm") ),
          strip.background = element_rect(fill = "white",linewidth = 0.35),
          strip.background.y =  element_blank(),
          strip.placement = "outside",
          legend.key.size = unit(0.1, 'in'),
                        legend.title = element_text(size = Fsize),
                        legend.text = element_text(size=Fsize-1),
          
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0  ),
          legend.position = "bottom"
    )
  print(plot)
}

```

##DE analysis (PTGER2Hi - PTGER2Lo)
Running time: 3.30 minutes (on Apple MacBook Air M2 16GB RAM, macOS 14.4.1)
Function FullDE() computes DE Genes between population A (PTGER2 Hi) and population B (PTGER2 Lo)
- Group: PTGER2 group name
- Batch: specimen ID
Expected output: a list with DE genes in each cell type

```{r}
DE = list()
Idents(Integrated) = Integrated$Identity.Celltype
selected.clusters = c("NK cell","CD8 T cell","CD4 T cell", "Regulatory T cell","Neutrophil","Monocyte")
for(i in selected.clusters ){
      print(i)
      tmp = subset(Integrated, idents = i)
      DE[[i]] = FullDE(tmp, Group = "PTGER2.Group", Batch = "ID" , A = "High", B = "Low" )
}
```

###Create a single table of DE genes 
```{r}
df = data.frame()
for(i in names(DE)){
  tmp = names(DE[[i]]) %>% setdiff(c("FoldChange.Table","FoldChange.Sum"))
  for(j in tmp ){
      df1 = DE[[i]][[j]] %>% as_tibble(rownames = "Genes")
      df1$Cluster = i
      df1$Dataset = j
      df = rbind(df,df1)
      }
}
df$Cluster = factor(df$Cluster, levels= names(DE) )
DE$df = df
```

###Plot Heatmap
```{r}
selected.cluster = c("CD8 T cell")
for(i in c("CD8.Overview3") ){
  selected.genes = unlist( GeneSet$DE[[i]] ) %>% unique()
  df1 = filter(df, Genes %in% selected.genes )  %>% filter(Cluster %in% selected.cluster)
  df1 = GeneGroup(df1, GeneSet$DE[[i]] )
  Fsize = 6
  a = max(abs(df1$avg_log2FC))+0.2 
  plot = ggplot(df1, aes(y = Dataset , x = Genes  ) ) + 
    facet_grid(Cluster ~ Set, scales = "free", space="free", switch = "y") + 
    theme_classic() + 
    Dot_axis90A + 
    ggtitle(i)+
    geom_tile(color = "white",aes(fill =avg_log2FC)) +  
    scale_fill_gradientn(colours = Col.HiLow.9Shades,
                         values =  c( 0,0.43,0.5,0.57,  1 ),                                 
                         limits = c(-a,a) ) +
    theme(plot.title = element_blank(),
          axis.text.x = element_text(size =Fsize, family = "Arial", color = "black", face = "italic",angle = 90, hjust =1, vjust =0.3),
          axis.text.y = element_text(size =Fsize, family = "Arial", color = "black"),
          axis.line = element_line(colour = 'black', size = 0.25),
          axis.ticks = element_line(colour = 'black', size = 0.15),
          axis.ticks.length = unit(0.05,"cm"),
          axis.title = element_blank(), 
          strip.text.y = element_blank(),
          strip.text.x.top = element_text(size =Fsize, family = "Arial",colour = "black",
                                          margin = margin(t = 0.1, r = 0, b = 0.1, l = 0, unit = "cm") ),
          strip.background = element_rect(fill = "white",linewidth = 0.35),
          strip.background.y =  element_blank(),
          strip.placement = "outside",
          legend.key.size = unit(0.1, 'in'),
                        legend.title = element_text(size = Fsize),
                        legend.text = element_text(size=Fsize-1),
          
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0  ),
          legend.position = "bottom"
    )
  print(plot)
}

```

